Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-08 manuscript.tex

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, produce thin proteic sheets wrapped concentircallu about the  \citep{schmidt_1939}

>>>>

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, produce thin protein sheets wrapped concentrically around the axon \citep{schmidt_1939}
